---
title: "Changing of the number of Marriage Licence for each Civic Center from 2011-2021"
author: 
  - Yiyi Feng
date: today
date-format: long
thanks: "Code and data are available at: https://github.com/kqlqkqlqF/Reflection-exercise-3."
format:
  pdf:
    toc: true
    number-sections: true
number-sections: true
abstract: "This exercise is for making a graph to demonstrate the pattern of the marriage license number for each civic center from 2011 ro 2021."
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(ggplot2)
library(dplyr)

#### Read data ####
data <-
  read_csv(
    file = "../data/analysis_data/analysis_marriage_data.csv",
    show_col_types = FALSE)
```


# Introduction

The data for this analysis was collected from the shared Toronto Open Database [@opendatatoronto], and the analysis was done by R [@citeR]. The [@fig-one] has demonstated the overall changes happening for the number of Marriage license, but have to say this is too crowded and we cannot see the tendency. So we made [@fig-two] which only demonstrated partially of the trend.


```{r}
#| label: fig-one
#| fig-cap: Number of Licenses of Marriage for each Civic Centre from 2011 to 2021
#| echo: false
#| message: false

# Grouping the data by date and CIVIC_CENTRE, summing the marriage licenses
total_licenses <- data %>%
  group_by(date, CIVIC_CENTRE) %>%
  summarize(Total_Licenses = sum(MARRIAGE_LICENSES), .groups = 'drop')

# Create the line plot
ggplot(total_licenses, aes(x = date, y = Total_Licenses, color = CIVIC_CENTRE)) +
  geom_line(size = 1) +
  labs(x = "Year", y = "Total Marriage Licenses", 
       title = "Marriage Licenses Over Time by Civic Centre") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
#| label: fig-two
#| fig-cap: Number of Licenses of Marriage for each Civic Centre from 2011 to 2013
#| echo: false
#| message: false

# Summarize total licenses, filtering for the desired date range (2011-2013)
total_licenses <- data %>%
  filter(date >= as.Date("2011-01-01") & date <= as.Date("2013-12-31")) %>%
  group_by(date, CIVIC_CENTRE) %>%
  summarize(Total_Licenses = sum(MARRIAGE_LICENSES, na.rm = TRUE), .groups = 'drop')

# Create the line plot
ggplot(total_licenses, aes(x = date, y = Total_Licenses, color = CIVIC_CENTRE)) +
  geom_line(linewidth = 1) +
  labs(x = "Year", y = "Total Marriage Licenses", 
       title = "Marriage Licenses Over Time by Civic Centre (2011-2013)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


\newpage


# References


